MSF_Groupwork-NBA_shotlog

### 2016-10-10 MSFGroupwork-NBAHotHand.Rmd
FG% analysis (not done yet)

#SUMMARY OF POINTS
```{r}
ptssum<- cast(df, GAME_ID1+ player_id + player_name ~ PTS); head(ptssum)
#creating "total points per player, per game" column
ptssum$totalpts<- ptssum[,"2"]*2 + ptssum[,"3"]*3

pttsum2<-ptssum[order(ptssum$totalpts,decreasing=TRUE),]
head(pttsum2,10)

### Home Advantage analysis
```{r}
# replacing W/L in column "W" with 1/0 (1 for win, 0 for loss)
df[,"W"] <- as.character(df[,"W"])

@@

@@

```
###Hot Hand Theory

```{r}
#Set the value to character
df[, "SHOT_RESULT"] <- as.character(df[, "SHOT_RESULT"])

#Define 1 for baskets made and 0 for baskets missed. We need a vector to use it to our function below.
shotresult <- c()
for(i in 1:nrow(df)) {
  if(shots[i] == 'missed') shotresult <- c(shotresult, 0)
  else if(shots[i] == 'made') shotresult <- c(shotresult, 1)
}

shotresult

#Set the value to numeric/integer
df[, "SHOT_RESULT"] <- as.numeric(df[, "SHOT_RESULT"])
df[ ,'SHOT_NUMBER'] <- as.integer(df[ , 'SHOT_NUMBER'])

#Create new column with shot results(1 for baskets made and 0 for baskets missed)
df[ ,'SHOTRESULT_0_1'] <- shotresult

#Define the length of a shooting streak to be the number of consecutive baskets made until a miss occurs
#Create a function that gives us a vector with the number of streaks
number_of_streaks <- function(x) {
  x <- c(0, x, 0)
  which_zero <- which(x == 0)
  streak <- diff(which_zero) - 1
  streak
}

number_of_streaks(shotresult)
#To be continued (probabilities- indipendence, plots, interpret results for specific players(those with higher shot_numbers))
```

>>>>

```
### Home Advantage analysis
```{r}
# replacing W/L in column "W" with 1/0 (1 for win, 0 for loss)
df[,"W"] <- as.character(df[,"W"])

@@

# Shooting Percentage Analysis (James)

```{r}
# Replace "made" and "missed" with 1 and 0 respectively

df[, "SHOT_RESULT"] <- as.character(df[, "SHOT_RESULT"])

for (i in 1:nrow(df)) {
  if (df[i, "SHOT_RESULT"] == "made") df[i, "SHOT_RESULT"] <- 1
  if (df[i, "SHOT_RESULT"] == "missed") df[i, "SHOT_RESULT"] <- 0
}

df[, "SHOT_RESULT"] <- as.numeric(df[, "SHOT_RESULT"])

@@
